Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-15 draft.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
    \caption{Distribution of the stellar mass of the SN host and field galaxies used in the analysis. }
    \label{fig:mass_hist_hosts_field}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host and field galaxies used in the analysis. Lower: As upper for field galaxies, but shown on a log scale.  The distribution is well described by a Schechter function.}
    \label{fig:mass_hist_hosts_field}
\end{figure}
